\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{geometry}
\geometry{left=1in,right=1in,top=1in,bottom=1in}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=blue,
    pdftitle={CV - Sang-hyun Kim},
}

\titleformat{\section}{\Large\bfseries\vspace{1ex}}{}{0em}{}[\titlerule]

\begin{document}

\begin{center}
    {\Huge \textbf{Sang-hyun Kim}} \\ \vspace{0.3cm}
    School of Mathematics \\
    Korea Institute for Advanced Study \\
    Professor and Chair, School of Mathematics, KIAS \\
    \href{mailto:kimsh@kias.re.kr}{kimsh@kias.re.kr} \quad \href{mailto:skim.math@gmail.com}{skim.math@gmail.com} \quad \href{https://kimsh.kr}{https://kimsh.kr}
\end{center}

\vspace{0.5cm}

\section*{Education}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Ph.D. Mathematics}, Yale University, May 2007. \\
    Dissertation: \textit{Surface subgroups of graph products of groups and right-angled Artin groups.} \\
    Thesis Advisor: Andrew J. Casson.
    \item \textbf{B.S. Mathematics}, Seoul National University, August 1997.
\end{itemize}

\section*{Fields of Interest}
Geometric group theory, low-dimensional topology.

\section*{Academic Positions}
\begin{itemize}[leftmargin=1.5em]
    \item \textbf{Professor}, Korea Institute for Advanced Study (KIAS), Feb 2019 -- present.
    \item \textbf{Chair}, School of Mathematics, KIAS, July 2024 -- present.
    \item \textbf{Affiliate Professor}, KAIST, Sep 2019 -- present.
    \item \textbf{Associate Professor}, Seoul National University, March 2014 -- Jan 2019.
    \item \textbf{Associate Professor}, KAIST, September 2013 -- February 2014.
    \item \textbf{Assistant Professor}, KAIST, June 2010 -- August 2013.
    \item \textbf{Norbert Wiener Assistant Professor}, Tufts University, September 2010 -- May 2011.
    \item \textbf{R. H. Bing Instructor}, the University of Texas at Austin, January 2008 -- August 2010.
    \item \textbf{Post-doctoral Fellow}, Mathematics Sciences Research Institute (MSRI), September -- December 2007.
\end{itemize}

\section*{Publications}
\subsection*{Published}
\begin{enumerate}[leftmargin=1.5em, label=\arabic*.]
\setcounter{enumi}{0}
\item Inhyeok Choi, Sang-hyun Kim, Smoothing countable group actions on metrizable spaces, to appear in Advanced Studies in Pure Mathematics (Proceedings of Mathematical Society of Japan - Seasonal Institute).
\item Sang-hyun Kim, Nicol\'as Matte Bon, Mikael de la Salle and Michele Triestino, Subexponential growth and $C^1$ actions on one-manifolds, International Mathematics Research Notices, Volume 2025, Issue 13, July 2025, rnaf202.
\item Sang-hyun Kim, Thomas Koberda and Javier de la Nuez-Gonzalez. First order rigidity of homeomorphism groups of manifolds, Comm. Amer. Math. Soc. 5 (2025), 144-194.
\item Nhat Minh Doan, Sang-hyun Kim, Mong Lung Lang, Ser Peow Tan. Optimal independent generating system for the congruence subgroups $\Gamma_0(p)$ and $\Gamma_0(pq)$, The Journal of Geometric Analysis (2025) 35:216
\item Sang-hyun Kim and Thomas Koberda. Non-freeness of groups generated by two parabolic elements with small rational parameters. Michigan Mathematical Journal (2022).
\item Sang-hyun Kim and Genevieve Walsh. Some groups with planar boundaries, Surveys in Differential Geometry (2022).
\item Sang-hyun Kim, Thomas Koberda and Crist\'obal Rivas. Virtual critical regularity of mapping class group actions on the circle, Transformation Groups (2022).
\item Sang-hyun Kim and Thomas Koberda. Structure and regularity of group actions on one-manifolds, Springer Monographs in Mathematics (2021).
\item Sang-hyun Kim, Thomas Koberda and Crist\'obal Rivas. Direct products, overlapping actions, and critical regularity, Journal of Modern Dynamics, Vol. 17 (June 2021), pp. 285-304.
\item Sang-hyun Kim, Thomas Koberda, Jaejeong Lee, Ken'ichi Ohshika and Ser Peow Tan; appendix by Xinghua Gao. Shapes of hyperbolic triangles and once-punctured torus groups, Mathematische Zeitschrift (2021).
\item Sang-hyun Kim and Thomas Koberda. Integrability of moduli and regularity of Denjoy counterexamples. Discrete and Continuous Dynamical Systems-A, October 2020, 40(10): 6061-6088.
\item Christian Bonatti, Sang-hyun Kim, Thomas Koberda and Michele Triestino. Small $C^1$ actions of semidirect products on compact manifolds, Algebraic \& Geometric Topology 20 (2020) 3183--3203.
\item Sang-hyun Kim and Thomas Koberda. Diffeomorphism groups of critical regularity. Inventiones mathematicae, 221(2), 421-501 (2020).
\item Sang-hyun Kim, Thomas Koberda and Mahan Mj, Flexibility of Group Actions on the Circle, Springer Lecture Notes in Mathematics 2231 (2019).
\item Sang-hyun Kim, Thomas Koberda and Yash Lodha, Chain groups of homeomorphisms of the interval and the circle, Annales Scientifiques de l'\'Ecole Normale Sup\'erieure, Series 4, Volume (52), 2019, 797-820.
\item Hyungryul Baik, Sang-hyun Kim and Thomas Koberda. Unsmoothable group actions on compact one-manifolds, Journal of European Mathematical Society, Volume 21, Issue 8, 2019, pp. 2333--2353.
\item Sang-hyun Kim and Thomas Koberda. Free products and algebraic structures of diffeomorphism groups, Journal of Topology, Volume 11, Issue 4, December 2018, Pages 1053-1075.
\item Sang-hyun Kim. Surface subgroups of word-hyperbolic groups (survey), Handbook of group actions. Vol. III, 89-102.
\item Sang-hyun Kim and Thomas Koberda. RAAGs in Diffeos (survey), Advanced Studies in Pure Mathematics: Volume 73, 215-224 (2017).
\item Cheol-Hyun Cho, Hansol Hong, Sang-hyun Kim and Siu-Cheong Lau. Lagrangian Floer potential of orbifold spheres, Advances in Mathematics, Volume 306, 14 January 2017, Pages 344-426.
\item Hyungryul Baik, Sang-hyun Kim and Thomas Koberda. Right-angled Artin groups in the $C^{\infty}$ diffeomorphism group of the real line, Israel Journal of Mathematics, June 2016, Volume 213, Issue 1, pp 175-182.
\item Sang-hyun Kim and Thomas Koberda. Right-angled Artin groups and finite subgraphs of curve graphs, Osaka Journal of Mathematics, Volume 53, Number 3 (2016), 705-716.
\item Sang-hyun Kim and Thomas Koberda. Anti-trees and right-angled Artin subgroups of braid groups, Geometry \& Topology 19-6 (2015), 3289--3306.
\item Sang-hyun Kim and Genevieve Walsh. Coxeter groups, hyperbolic cubes, and acute triangulations, Journal of Topology (2016) 9 (1): 117-142.
\item Sang-hyun Kim and Thomas Koberda. The geometry of the curve complex of a right-angled Artin group, International Journal of Algebra and Computation (2014) 24 (2) 121-169.
\item Sang-hyun Kim and Sang-il Oum. Hyperbolic Surface subgroups of one-ended doubles of free groups, Journal of Topology (2014) 7 (4): 927--947.
\item Sang-hyun Kim and Thomas Koberda. An obstruction to embedding right-angled Artin groups in mapping class groups, International Mathematics Research Notices (2014) \#2014 (14): 3912--3918.
\item Sang-hyun Kim and Thomas Koberda. Embeddability between right-angled Artin groups, Geometry \& Topology 17 (2013) 493--530.
\item Sang-hyun Kim and Henry Wilton. Polygonal words in free groups, Quarterly Journal of Mathematics (2012) 63(2), 399--421.
\item Sang-hyun Kim. Surface subgroups of graph products of groups, International Journal of Algebra and Computation (2012) 22 (8).
\item Sang-hyun Kim. Geometricity and polygonality in free groups, International Journal of Algebra and Computation 21(1--2) (2011) 235--256.
\item Sang-hyun Kim. On right-angled Artin groups without surface subgroups, Groups, Geometry, and Dynamics 4(2) (2010) 275--307.
\item Chan-Byoung Chae, Sang-hyun Kim and Robert W. Heath Jr., Linear network coordinated beamforming for cell-boundary users, Proc. of IEEE Workshop on Signal Processing Advances in Wireless Communications (SPAWC) (2009).
\item Chan-Byoung Chae, Sang-hyun Kim and Robert W. Heath Jr., Network coordinated beamforming for cell-boundary users: linear and non-linear approaches, IEEE Journal of Selected Topics in Signal Processing (J-STSP), vol. 3, no. 6 (2009) 1094--1105.
\item Sang-hyun Kim. Co-contractions of graphs and right-angled Artin groups, Algebraic and Geometric Topology 8 (2008) 849--868.
\end{enumerate}

\subsection*{Accepted/Submitted}
\begin{enumerate}[leftmargin=1.5em, label=\arabic*.]
\item TBA on Samurai (2026).
\item Aletheia tackles FirstProof autonomously (2026).
\item Towards Autonomous Mathematics Research (2026).
\item Semi-Autonomous Mathematics Discovery with Gemini: A Case Study on the Erd\H{o}s Problems (2026).
\item Irrationality of rapidly converging series: a problem of Erd\H{o}s and Graham (2026).
\item Elementary equivalence and diffeomorphism groups of smooth manifolds (2025).
\item Jaewon Chang, Sang-hyun Kim and Thomas Koberda. Algebraic Structure of Diffeomorphism Groups of One-Manifolds, accepted, Panoramas et synth\`eses - Soci\'et\'e math\'ematique de France.
\end{enumerate}

\subsection*{Notes unpublished}
\begin{enumerate}[leftmargin=1.5em, label=\arabic*.]
\item Sang-hyun Kim, Thomas Koberda and Juyoung Lee. Finite subgraphs of extension graphs.
\item The Arens space $S_2$ is a paracomplex: A note on Nagata's Problem 3.
\end{enumerate}

\subsection*{For general public}
\begin{enumerate}[leftmargin=1.5em, label=\arabic*.]
\item Sang-hyun Kim. Scientific Walks, Joongang-ilbo, June 2023 - June 2025: a newspaper column series appearing every three weeks.
\item Sang-hyun Kim. Turing and the Halting Problem, Horizon (a KIAS magazine, in Korean), 2021.
\item Sang-hyun Kim. Mathematics and Imagination (in Korean), Korean Educational Broadcasting System Publication, 2022: a book based on the series of eleven TV public lectures.
\item Sang-hyun Kim. A group seen from its boundary, Horizon (a KIAS magazine, in Korean), 2019.
\end{enumerate}

\section*{Honors and Awards}
\begin{itemize}[leftmargin=1.5em]
\item The Choi Seok-jeong Award, by the Korean Ministry of Science and ICT, November 2023.
\item The Scientist and Engineer of the Month, by the Korean Ministry of Science and ICT, July 2020.
\item Y-KAST Member, by the Korean Academy of Science and Technology (KAST), 2018 -- 2021.
\item Research Excellence Award, College of Natural Sciences, Seoul National University, March 3, 2017.
\item Excellent Research Paper Award, Korean Mathematical Society, April 23, 2016.
\item Teaching Excellence Award, College of Natural Sciences, Seoul National University, Sep 15 2015.
\item Creative Teaching Grand Award, KAIST, Feb 15, 2013.
\item Sang-San Prize for Young Mathematicians, Korean Mathematical Society, October 5, 2012.
\item R. H. Bing Fellowship, the University of Texas at Austin, 2008 -- 2010.
\item Silver medal, the 34th International Mathematical Olympiad, Turkey, 1993.
\end{itemize}

\section*{Grants}
\begin{itemize}[leftmargin=1.5em]
\item Principal Investigator (single), Samsung Science \& Technology Foundation Research Grant, 2014 -- 2018, 2019 -- 2023.
\item Principal Investigator (single), Basic Science Research Program, NRF, 2010 -- 2013, 2013 -- 2016.
\item Joint Investigator (with Suhyoung Choi and Kihyoung Ko), Mid-Career Researcher Program, NRF, 2010 -- 2013.
\item Principal Investigator (single), Mid-Career Researcher Program, NRF, 2018 -- 2021 and 2023 -- 2028.
\end{itemize}

\section*{Professional Activities}
\subsection*{Journals}
\begin{itemize}[leftmargin=1.5em]
\item Editor, KIAS-Springer Series in Mathematics, 2020 -- present.
\item Editor, Journal of Korean Mathematical Society, 2019 -- present.
\item Editor, HORIZON (KIAS webzine for general public), 2022 -- 2025.
\item Reviewer, MR (Mathematical Reviews) and zbMATH.
\end{itemize}

\subsection*{Services (recent)}
\begin{itemize}[leftmargin=1.5em]
\item KIAS PR Committee, 2025 -- present.
\item KIAS Transdisciplinary Research, Program Committee, 2023 -- present.
\item Chair, School of Mathematics, KIAS, 2024 -- present.
\item Mentor, Vietnam Polymath REU, 2023 -- 2024.
\item Section Committee (Topology), Korean Mathematical Society, 2023 -- present.
\item Review Board, National Research Foundation of Korea, 2018 -- 2022.
\item Research Output Analysis Committee, National Research Foundation of Korea, 2020 -- 2022.
\item Steering Committee, Seoul Science High School, 2018 -- 2020.
\item Executive board member, Korean Mathematical Society, 2013 -- 2014.
\end{itemize}

\subsection*{Seminars currently organized}
\begin{itemize}[leftmargin=1.5em]
\item Virtual Seminar on Geometry And Topology (visgat)
\item Geometric Group Theory in East Asia (GGTEA)
\end{itemize}

\subsection*{Conferences organized / Committees}
\begin{itemize}[leftmargin=1.5em]
\item Geometric and Asymptotic Group Theory with Applications (GAGTA), annual. Scientific Committee (2023), Steering Committee (2023-present).
\item East Asian School of Geometric Topology (EACGT), annual. Program Committee (2018-present).
\item Young Geometric Group Theory (yGGT) XIV, KIAS, June 8-12 2026.
\item Organizer, Dynamical Group Theory series (I through VIII, 2023-2026).
\item Mapping Class Groups @KIAS, October 13-17, 2025.
\item Current Challenges in Mathematics, August 25-29, 2025.
\item 2K-Gate I, June 10-13, 2025.
\item Organizer, Korean Mathematical Society Fall Meeting, Topology I Session, Oct 22-23, 2025.
\item Organizer, KIAS Graduate Student Meeting in Pure Mathematics, October 21st, 2024.
\item Organizer, Hyperbolic Geometry of Numbers, Dec 18 - 20, 2023.
\end{itemize}

\section*{Teaching Experiences}
\textbf{Seoul National University}: Algebraic Structure of Diffeomorphism Groups (Spring 2018), Dynamics on the Circle (Spring 2016), Geometry on Infinite Groups (Fall 2014), Calculus 1 and 2 (Spring/Fall 2015, 2018), Topology 1, 2 (Spring/Fall 2015), Mathematics for Biology 1, 2 (Spring/Fall 2016), Algebraic Topology 1 (Fall 2016, 2018). \\
\textbf{KAIST}: Groups and Dynamics (Spring 2022), Education 3.0 Calculus I (Spring 2012, 2013), Education 3.0 Calculus II (Fall 2012), Algebraic Topology I (Spring 2013), Groups, Graphs and Geometry (Spring 2012), Calculus II (Fall 2011), Freshman Seminar (Fall 2011). \\
\textbf{Tufts University}: Calculus II (Fall 2010), Calculus III (Fall 2010, Spring 2011). \\
\textbf{University of Texas at Austin}: Differential and Integral Calculus I (Spring 2008, Fall 2008, 2009), Differential and Integral Calculus II (Spring 2010), Introduction to Number Theory (Summer 2009), Probability I (Summer 2008, Spring 2009), Discrete Math (Spring 2008), Topics in Geometric Group Theory (Spring 2010). \\
\textbf{Yale University}: Calculus of Functions of One Variable (2006, 2007), Introduction to Functions of Several Variables (2006), Calculus of Functions of Several Variables (2001-2006).

\section*{Talks}
\begin{enumerate}[leftmargin=1.5em, label=\arabic*.]
\item New Developments of Teichmüller Theory (Oberwolfach Workshop), September 28 - Oct 2, 2026.
\item Busan Mathematics Culture Center, July 10, 2026.
\item Kangwon Cultural Education Center, May 6, 2026.
\item CRUNCH seminar, April 24, 2026.
\item Daegu Gosan Library, April 10, 2026.
\item Current Challenges in Topology, Milan, Italy, May 20 - 24, 2026.
\item EBS, March 18, 2026.
\item IMU-KIAS Colloquia, hosted with the IMU Executive Committee, KIAS, March 11 - 13, 2026.
\item Military TV, March 11, 2026.
\item Career Lecture at the Graduation Ceremony, the Gifted Education Center, the Chungcheongbuk-do Institute of Science Education, October 18, 2025.
\item The 6th Workshop on Geometry and Topology around Young-Nam, September 26 - 27, 2025.
\item Hyundai Motor Group, August 13, 19, 26, 2025.
\item Topology seminar, National University of Singapore, July 30, 2025.
\item Non-positive curvature and applications, Isaac Newton Institute, July 7 - 11, 2025.
\item Daejeon Institute of Education Information, June 26, 2025. (public math, "human, mathematics and computer")
\item Geometric Group Theory and Related Topics, June 16 - 20, 2025, BICMR. [Link]
\item Mathematics Colloquium, April 16 (Wed), 2025, Kyungpook National University
\item East Asian Conference on Geometric Topology 20, Tokyo, Japan, February 4, 2025.
\item Friday Seminar on Knot Theory, OCAMI, Osaka, Japan, January 31, 2025.
\item What is...? (on rotation number), Osaka University, Japan, January 30, 2025.
\item 2025 KMS-VMS Joint Workshop, Hanoi, Vietnam, January 6 - 10, 2025.
\item Geometry and Dynamics in Low-Dimensions, Hanoi, Vietnam, Janury 6 - 10, 2025.
\item On Dream Young Mathematicians Camp (for high school students), January 5, 2025.
\item Topology Seminar, National University of Singapore, December 26, 2024.
\item Foliations and Diffeomorphism Groups, CIRM, Marseille, December 9 - 13, 2024.
\item Dynamical Group Theory V (KOREA: KIAS workshop on One RElator groups and other Aspects of GGT), September 27, 2024. [Link]
\item KAIST, Basic Science Week, October 30, 2024.
\item Davinci Motel by Hyundai Card, Seoul, September 28, 2024. (public math, invitation- only meeting)
\item Dynamical Group Theory IV (KIAS-Rice Workshop), September 27, 2024. [Link]
\item Public Lecture, Huh June Center for Mathematical Challenges, September 7, 2024. [Link]
\item Colloquium, Huh June Center for Mathematical Challenges, September 5, 2024.
\item Public Lecture organized by Korea Academy of Science and Technology (KAST), Seoul Science High School, August 19, 2024.
\item Panel Discussion, World Congress of Korean and Korean-Ethnic Scientists and Engineers, Seoul, July 11, 2024.
\item KFAS Summer 2024, Gangneung, Korea, July 4 - 6, 2024.
\item KAOS Science, "100 years of geometric topology and the Poincaré conjecture", July 3, 2024 [Stream Link] (recording: June 17)
\item REU Colloquium, University of Virginia, June 19, 2024 (8 PM, US EST) / June 20, 2024 (9 AM, KST) : online.
\item Computational aspects of thin groups, Institute for Mathematical Sciences National University of Singapore, June 11, 2024.
\item An-ahm Lecture, Korea University, May 20, 2024
\item Low Dimensional Actions, IHP (Institute Henri Poincaré), Paris, April 29 - May 3,
\item [Link]
\item Oberseminar Differentialgeometrie, Max Planck Institute for Mathematics, April 25,
\item [Link]
\item Special Session on Geometric Structures and Representation Spaces, Korean Mathematical Society , KAIST, Daejeon, April 20, 2024.
\item Colloquium, KRIMS, Kangwon University, April 17, 2024.
\item Math Colloquium, Postech, Pohang, March 22, 2024. [Link]
\item The 19th East Asian Conference of Geometric Topology, Kyoto, Japan, February 19 - 23, 2024.
\item KAIST Geometric Topology Fair 2024, Busan, Jan 15 - 19, 2024
\item Round table discussion on publicizing science culture, Ministry of Science and ICT, Korea, January 10, 2024, [news]
\item "What is a good mathematical research?", The Third Round Table -- Mathematics for Tomorrow, old and new", The Korean Federation of Science and Technology Societies (KOFST), Korea, December 20, 2023 [YouTube]
\item Department Colloquium, Yonsei University, Seoul, Korea, November 9, 2023 (5 pm).
\item Dream Lecture Series by Korea Foundation for Advanced Studies, West Daejeon Highschool, Oct 18, 2023.
\item The 4th Korea-France Conference in Mathematics, August 21 - 25, 2023, KIAS, Korea.
\item Teichmüller Theory: Classical, Higher, Super and Quantum, Mathematisches Forschungsinstitut Oberwolfach, Germany, July 30 - Aug 4, 2023. Title: Optimal independent system for Gamma0(p) and Gamma0(pq).
\item Characters and Moduli of Surfaces (SerFest), The Research Institute for Mathematical Sciences (RIMS), Kyoto, Japan, July 19 - 21, 2023.
\item The Mathematical Society of Japan -- Seasonal Institute (MSJ-SI), New aspects of Teichmüller theory, University of Tokyo, Japan, July 9 - 15, 2023.
\item Korea Foundation for the Advancement Science \& Creativity, International Olympiad Team Ceremony, June 14, 2023.
\item NCTS 2023 dynamics workshop (minicourse of 3 talks), National Center for Theoretical Sciences (NCTS), National Taiwan University, Taiwan, June 8-10, 2023.
\item Topology Seminar, Gakushuin University, May 26, 2023.
\item Special Session on Geometric Structures and Representation Spaces, Korean Mathematical Society , April 28, 2023.
\item Topology seminar, Seoul National University, April 21, 2023.
\item The 3rd Probabilistic Methods in Negative Curvature workshop  (minicourse of 4 talks), ICTS Bangalore, India, February 27 -- March 10, 2023 (mini-course).
\item Conformal dynamics and groups, BICMR, December 2, 2022 (online).
\item The Pacific Rim Mathematical Association Congress 2022 (PRIMA CONGRESS 2022), Vancouver, Canada, Special Session on ``Geometric Group Theory'', December 2022 (TBD).
\item School on Dynamical Group Theory, Dijon, France, Oct 3 - 7, 2022 (mini-course of 3 talks).
\item Mathematics Department Colloquium, Sookmyung Women's University, September 15, 2022.
\item REU Colloquium, University of Virginia, July 27, 2022 (US EST) / July 28, 2022 (KST) : online.
\item Topology and Geometry Seminar, National University of Singapore, July 4, 2022.
\item Regular Workshop, Integrative Research Institute in Basic Science, Soongsil University, June 24, 2022.
\item Geometry and Analysis on Groups Research Seminar, University of Vienna, June 7,
\item 
\item OpenKIAS Public Lecture, Korean Mathematical Society, April 28, 2022 (5pm), hybrid.
\item "공간의 풍경 (The landscape of a space), KIAS Public Lecture, Korean Mathematical Society Spring Meeting, April 28, 2022. [Youtube]
\item Sydney Mathematical Research Institute (SMRI) Algebra and Geometry Online seminar, March 2nd, 2022 (Wed, 11 am KST/ 1 pm Australia). [youtube]
\item Future intelligence (forum), CHUNG MONG-KOO Foundation and Chosun Ilbo, February 17, 2022. [youtube] [youtube (sketch)] [news article]
\item Samsung Sciences \& Technology Foundation Annual Forum, November 22, 2021.
\item Geometry and Topology Online, Warwick Mathematics Institute, November 18, 2021 (online).
\item Human, Mathematics, Computer (On the Halting problem of Turing), KFAS building, Dream Lecture Series by Korea Foundation for Advanced Studies, November 13,
\item 
\item Symmetry in Newcastle (seminar), The University of Newcastle, Australia, November 1, 2021 (online). [youtube]
\item Graduate seminar on mathematical challenges, Yonsei University, October 6, 2021.
\item VI Congreso Latinoamericano de Matemáticos (CLAM) 2021, Montevideo, Uruguay, September 14, 2021 (online).
\item REU Colloquium, University of Virginia, July 21, 2021 (online).
\item Mathematical Sciences Department colloquium, Seoul National University, May 6,
\item "On Circle Diffeomorphism Groups" (online).
\item The 16th East Asian Conference on Geometric Topology, University of Tokyo, Japan, January 25, 2021. (online, invited talk)
\item OpenKIAS public lecture - 불가능에 대하여 (갈루아, 괴델, 튜링, 힐버트), December 22, 2020. [Youtube]
\item Expanding Dynamics, CMM - Center for Mathematical Modeling / Universidad de Chile, October 13, 2020. (online)
\item Teichmüller Theory: Classical, Higher, Super and Quantum, CIRM, Luminy, France, October 8, 2020. (online)
\item The 3rd International Undergraduate Mathematics Summer School, Seoul National University,TBD, 5 lectures, postponed.
\item Mathematics Colloquium, Seoul National University, Korea, TBD. Groups of circle diffeomorphisms: analysis, dynamics and algebra, postponed.
\item 이토록 황홀한 수학 (Fascinated by Mathematics), a series of 11 lectures on various subjects, EBS2 channel (Korean Educational Broadcasting System), August 19 - September 2, 2020. lecture 1 (youtube)  complete lectures
\item REU Colloquium, University of Virginia, June 24, 2020 (online).
\item Colloquium at Electrical Engineering School, DGIST, Korea, June 2, 2020 (online).
\item Hyperbolic Lunch, University of Toronto, May 13, 2020. (online)
\item Virtual Seminar on Geometry and Topology (visgat), KIAS and KAIST, March 31,
\item (online)
\item Topology Seminar, Gakushuin University, December 2, 2019.
\item Mathematics Colloquium, KAIST, November 21, 2019.
\item Mathematics Colloquium, Korea University, November 15, 2019.
\item Arbeitsgemeinschaft: Zimmer's Conjecture, Mathematisches Forschungsinstitut Oberwolfach, Germany, 13 -- 18 October, 2019. Title: Property T and actions on S\^1.
\item Geometry and Analysis on Groups Seminar, University of Vienna, Austria, October 8,
\item 
\item Summer School on Geometric Topology and Algebraic Geometry, KAIST, Korea, August 12 an 13, 2019.
\item Combinatorial and algebraic aspects of geometric structures – Workshop in Thailand, with the cooperation of Luxembourg, Singapore, and Thailand, Chiang Mai, Thailand, July 18 and 19, 2019.
\item Ordered Groups and Rigidity in Dynamics and Topology, Oaxaca, Mexico, June 17,
\item 
\item Undergraduate seminar, Kwangwoon University, June 7, 2019.
\item International Conference Complex Analysis, Partial Differential Equations And Their Applications, Hanoi, Vietnam, June 5, 2019. *My talk was on June 5, but it did not appear in the webpage for some reason.
\item Ergodic and Geometric Group (EGG) Theory seminar, EPFL, Lausanne, Swiss, May 27, 2019.
\item Non-positive curvature, Warsaw, Poland, May 20, 2019.
\item Geometry and Analysis on Groups Seminar, University of Vienna, Austria, May 16,
\item 
\item Public lecture at Mathematics Culture Festival, Gwachun National Science Museum, Korea, April 27, 2019.
\item Public lecture (organized by The Korean Academy of Science and Technology), Yeongnam High School, Daegu, Korea, April 3, 2019.
\item Special Sessions on Mapping Class Groups, University of Hawaii at Manoa, Honolulu, US, March 23, 2019.
\item The 14th East Asian Conference of Geometric Topology, Beijing, China, January 23,
\item (plenary)
\item Suzhou 2019 Workshop on Geometry Topology, Soochow University, Suzhou, China, January 18, 2019.
\item Boundaries of topological groups, C*-algebras, symmetric spaces, and Lyapounov exponents, TSIMF, Sanya, China, December 20, 2018.
\item One-day Workshop about Dynamics, Geometry and Groups, Suwon, Korea, December 5, 2018.
\item KIAS Analysis Seminar, Seoul, Korea, November 1, 2018.
\item New Trends in Teichmüller Theory and Mapping Class Groups, Mathematisches Forschungsinstitut Oberwolfach, Germany, September 2--8, 2018.
\item Department Seminar, Chiang Mai University, Thailand, August 24, 2018.
\item Talk concert (for general public), Gwachun National Science Museum, Korea, Aug 19,
\item 
\item Science Camp, College of Natural Sciences, Seoul National University, (1) August 3, 2016 (2) August 9, 2018.
\item International Conference on Dynamical Systems, Sustech, China, June 25--28, 2018. Slide (PDF)
\item Hyperbolic 3-manifolds and related topics, Postech, Korea, June 18-- 22, 2018.
\item Silk Road Geometry Conference, Gokova Geometry/Topology Institute (GGTI), Turkey, June 4 - 8, 2018.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Hanyoung Foreign Language High School, May 14, 2018.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, KFAS building, May 12, 2018.
\item Topology in Australia and South Korea, IBS-CGP, Korea, April 25--27, 2018.
\item KIAS (Korea Institute for Advanced Study), Korea, April 17, 2018.
\item Topology Seminar, KAIST, Korea, March 27, 2018.
\item Branched Coverings, Degenerations, and Related Topics 2018 (minicourse), Hiroshima University, Japan, March 5 - 9, 2018.
\item Structure of 3-manifold Groups, CIRM (Luminy), France, February 26 - March 2,
\item 
\item Workshop on Geometric Group Theory (minicourse), BICMR, Beijing University, December 16 - 17, 2017.
\item Kyoto University, December 12, 2017.
\item Low-dimensional topology seminar, Osaka University, December 5, 2017.
\item Topology Seminar, University of Tokyo, November 28, 2017.
\item Max Dehn Seminar, University of Utah, October 25, 2017.
\item Topology Seminar, Rice University, October 23, 2017.
\item Topology Seminar, University of Texas at Austin, October 20, 2017.
\item Colloquium, University of Virginia, October 12, 2017.
\item Geometric Group Theory and Topology Seminar, Tufts University, October 3, 2017.
\item Geometry and Topology Seminar, Brown University, September 29, 2017.
\item GGT Seminar, MgGill University, September 27, 2017.
\item Japan Conference on Discrete and Computational Geometry, Graphs, and Games: JCDCG3, Tokyo University of Science (Aug 29 - Sep 1), Tokyo, Japan, August 29,
\item 
\item Japanese Topology Symposium, Tokai University, Tokyo, Japan, August 21 -- 24, 2017, 2017.
\item Invited talk, Korea Institute for Advanced Study (KIAS), Korea, Aug 7, 2017.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, KFAS building, July 15, 2017.
\item GAGTA 2017: Geometric and Asymptotic Group Theory with Applications (July 3 -- 7), Bilbao, Spain, July 4, 2017.
\item SFB Seminar, Universität Regensburg, Germany, June 30, 2017.
\item Séminaire Géométrie, Dynamique et Topologie (GDT), L’Institut de Mathématiques de Marseille (I2M), France, May 22, 2017.
\item Geometry Seminar, ETH Zürich, Swiss, May 3, 2017.
\item Ergodic and Geometric Group (EGG) Theory seminar, EPFL, Lausanne, Swiss, April 27, 2017.
\item Thursday Colloquium, TIFR, Mumbai, India, April 20, 2017.
\item IBS--CGP Seminar, Pohang, Korea, April 13, 2017.
\item Department Colloquium, Sungkyunkwan University, Suwon, Korea, April 6, 2017.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Young-rak High School, March 20, 2017.
\item Topology--Geometry Seminar, Hiroshima University, Japan, March 16, 2017.
\item Topology Seminar, Osaka University, Japan, March 13, 2017.
\item Young Mathematicians' Camp, National Institute for Mathematical Sciences, Daejeon, February 22, 2017.
\item SNU Geometry and Topology Mini-Workshop, Seoul National University, Korea, February 17, 2017.
\item College of Natural Sciences Public Lecture, Seoul National University, Korea, February 9, 2017. [youtube]
\item SNU Topology Winter School, December 16,, 2016.
\item Virginia Topology Conference, University of Virginia, November 18, 2016.
\item Geometry and Topology Seminar, Seoul National University, November 16, 2016.
\item Topology Seminar, Sungkyunkwan University, November 15, 2016.
\item Invited Talk, Korean Mathematical Society Annual Fall Conference, October 22, 2016.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Seoul High School, October 14, 2016.
\item Workshop on Moduli Spaces of Geometric Structures, a part of the summer-long program Geometry, Topology and Dynamics of Moduli Spaces, National University of Singapore, August 17, 2016.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, KFAS building, July 23, and July 30, 2016.
\item Geometric Topology Fair 2016, KAIST, Daejeon, July 7, 2016.
\item GAGTA (Geometric and Asymptotic Group Theory and Applications) 2016, Stevens Institute of Technology, June 17, 2016.
\item IBS--CGP seminar, IBS--CGP, Pohang, Korea, April 21, 2016.
\item Saturday Public Science Lectures, College of Natural Sciences, Seoul National University, March 26, 2016.
\item Mathematics seminar, Konkuk University, Seoul, Korea, March 25, 2016.
\item Invited lecture, Korea Institute for Advanced Study (KIAS), Korea, Mar 2, 2016.
\item Group actions seminar, Yale University, Feb 22, 2016.
\item Geometry and topology seminar, Univ. of Massachusetts at Amherst, Feb 19, 2016.
\item Geometric group theory seminar, Tufts University, Feb 18, 2016.
\item Teichmüller theory and low-dimensional topology, Tsinghua Sanya International Mathematics Forum (TSIMF), China, Jan 11 - 15, 2016.
\item East Asian Conference on Algebraic Topology 6 (EACAT-6), Daejeon, November 30 - Dec 4, 2015.
\item 2015 International Workshop on Mathematical Sciences in Dalian, China, Oct 30 - Nov 1, 2015.
\item Saturday Public Science Lecture, College of Natural Sciences, Seoul National University, Oct 24, 2015.
\item Department Colloquium, Ewha Women's University, Oct 15, 2015.
\item University of Rennes, France, October 1, 2015.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Chil-won High School - October 16, 2015.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Seo-oon Middle School - September 4, 2015.
\item IBS--CGP Mathematics Festival for Undergraduates, Aug 17 - 21, 2015.
\item Dubrovnik VIII - Geometric Topology, Geometric Group Theory and Dynamical Systems, Croatia, June 22 - 26, 2015.
\item Statistics seminar, Seoul National University, Korea, June 4, 2015.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Seocho High School - May 29, 2015.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Kyungshin High School - May 8, 2015.
\item Geometry \& Topology seminar, Postech, Korea, April 22, 2015.
\item Geometric Group Theory on Gulf Coast (G\^3), San Padres Island, USA, March 26 - 29, 2015.
\item KIAS Algebra Seminar, KIAS, January 5, 2015.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, KFAS building, December 20, 2014.
\item Group Action Forum, Tsinghua Sanya International Mathematics Forum, China, December 15 -- 19, 2014.
\item KIAS/CMC Colloquium, KIAS, December 2, 2014.
\item Department Colloquium, Chiang Mai University, October 28, 2014.
\item Dream Lecture Series by Korea Foundation for Advanced Studies, Banpo High School, September 13, 2014.
\item the 7th Mathematical Society of Japan -- Seasonal Institute (MSJ-SI), Hyperbolic Geometry and Geometric Group Theory (ICM Satellite), University of Tokyo, Japan, July 30 - August 5, 2014.
\item Discrete Groups and Geometric Structures with Applications V , KU Leuven, Belgium, June 2 - 6, 2014.
\item Seoul National University Department Colloquium, Subgroups of Mapping Class Groups, March 13, 2014
\item Branched Coverings, Degenerations, and Related Topics 2014, Hiroshima University, Japan, March 7, 2014.
\item Groups and Geometry in the South East, Mathematics Institute, Warwick University, United Kingdom, February 21, 2014.
\item Complex Analysis and Topology of Discrete Groups and Hyperbolic Spaces, Research Institute for Mathematical Sciences, Kyoto University, Japan, January 24, 2014.
\item 5th East Asian Conference of Algebraic Topology (EACAT 5), Chinese Academy of Sciences, Beijing, China, December 3, 2013.
\item Wasatch Topology Conference, the University of Utah, USA, November 16, 2013.
\item Topology Seminar, University of Texas at Austin, November 11, 2013.
\item Geometry and Topology Seminar, City University of New York, November 5, 2013.
\item Discovery-oriented class in calculus, Inha University Pedagogy Workshop, October 28, 2013.
\item Korean Mathematical Society Annual Meeting, University of Seoul, Korea, October 25, 2013.
\item Geometry and Topology Seminar, Brown University, October 9, 2013.
\item Topology/Geometry Seminar, Yale University, October 8, 2013.
\item New York Applied Algebra Colloquium, City University of New York, 27 September,
\item 
\item Geometric and Analytic Group Theory, Ventotene Island, Italy, September 9-14, 2013.
\item Geometric Structures on Low-Dimensional Manifolds, Korea Institute for Advanced Study, Korea, May 24, 2013.
\item Discrete Math Seminar, KAIST, April 19, 2013.
\item Hot Topics: Surface subgroups and cube complexes, Mathematical Sciences Research Institute, USA, March 19, 2013.
\item Topology and Geometry Seminar, National University of Singapore, February 13,
\item 
\item Geometric Group Theory and Topology Seminar, Tufts University, January 29, 2013.
\item Topology/Geometry Seminar, Yale University, January 22, 2013.
\item Manhattan Algebra Day, Stevens Institute, USA, December 7, 2012.
\item Topology Seminar, Osaka University, December 4 2012.
\item Friday Workshop on Geometry of Artin Groups, KIAS, November 23, 2012.
\item Topology Seminar, Hanyang University, October 19 and October 26, 2012.
\item Department Colloquium, Sogang University, October 18 2012.
\item MSJ-KMS Joint Meeting, Kyushu University, Japan, September 17, 2012.
\item Topology Seminar, KAIST, September 5 2012.
\item The 10th KAIST Geometric Topology Fair, KAIST, Daejeon, Korea, August 16, 2012.
\item Geometric and Asymptotic Group Theory with Applications (GAGTA-6), University of Duesseldorf, July 30, 2012.
\item Geometric Group Theory - Kyoto 2012, Kyoto University, Japan, June 7, 2012.
\item Department Colloquium, Ulsan University, April 12 2012.
\item Workshop on Immersed surfaces in 3-manifolds, a part of the IHP program "Geometry and analysis of surface group representations", IHP, Paris, March 26, 2012.
\item Geometry and Topology Seminar, SUNY Buffalo, January 25, 2012.
\item AMS-MAA Joint Meeting, Special session on hyperbolicity in manifolds and groups, Boston, January 4, 2012.
\item Department Colloquium, Konkuk University, Seoul, Korea, November 17, 2011.
\item Department Colloquium, Hanyang University, Seoul, Korea, November 4, 2011.
\item Department Colloquium, Yonsei University, Seoul, Korea, October 13, 2011.
\item Department Colloquium, Seoul National University, Seoul, Korea, September 29,
\item 
\item The 4th Topology Workshop, Chonbuk National University, Jeonju, Korea, August 23 - 24, 2011.
\item The 9th KAIST Geometric Topology Fair, KAIST, Daejeon, Korea, August 9, 2011.
\item Geometric and Asymptotic Group Theory with Applications (GAGTA--5), Universitat Politecnica de Catalunya, Barcelona, Spain, July 12, 2011.
\item Dubrovnik VII - Geometric Topology, Inter-University Centre and University of Zagreb, Dubrovnik, Croatia, July 2, 2011.
\item Geometry/Topology Seminar, University of Chicago, April 12, 2011.
\item Topology/Geometry Seminar, Yale University, April 5, 2011.
\item Spring Topology and Dynamics Conference, University of Texas at Tyler, U.S.A., March 18, 2011.
\item AMS Southeastern Section Meeting, Special Session on Geometric Group Theory, Georgia Southern University, U.S.A., March 13, 2011.
\item Topology and Geometric Group Theory Seminar, Cornell University, March 8, 2011.
\item Bernstein Seminar, Cornell University, March 8, 2011.
\item AMS-MAA Joint Meeting, Special session on groups, geometry and applications, New Orleans, January 7, 2011.
\item Topology Seminar, KAIST, Korea, December 23, 2010.
\item Geometry and Topology Seminar, SUNY Buffalo, November 19, 2010.
\item Topology Seminar, University of Texas at Austin, November 8, 2010.
\item Geometry and Topology Seminar, Caltech, October 22, 2010.
\item Approaches to Group Theory, Using Algebraic, Analytic, and Geometric Tools in the Study of Groups, Cornell University, U.S.A., October 10, 2010.
\item Topology Seminar, Brandeis University, September 21 2010.
\item Geometric Group Theory and Topology Seminar, Tufts University, September 14,
\item 
\item KAIST Topology Workshop, Daejeon, Korea, August 4, 2010.
\item KAIST--POSTECH--SNU YB Workshop, Jeonju, Korea, July 3, 2010.
\item Topology Seminar, University of California at Santa Barbara, May 18, 2010.
\item AMS Special Session on Geometric Group Theory, University of New Mexico, U.S.A., April 18 2010.
\item Geometric Group Theory Seminar, Tufts University, January 19, 2010.
\item BK21 Seminar, KAIST, January 26 2010.
\item Joint Topology and Discrete Math Seminar, KAIST, December 28, 2009.
\item Topology Seminar, Konkuk University, December 22, 2009.
\item Joint Meeting of Korean Mathematical Society and American Mathematical Society, Special Session on Geometric Structures and Geometric Group Theory, Ewha Womans University, Korea, December 18, 2009.
\item Topology/Geometry Seminar, Yale University, October 27, 2009.
\item Topology Seminar, The University of Texas at Austin, August 31, 2009.
\item International Conference on Geometric and Combinatorial Methods in Group Theory and Semigroup Theory, the University of Nebraska-Lincoln, U.S.A., May 20, 2009.
\item AMS Special Session on Recent Progress in Geometric Group Theory, San Francisco State University, April 25, 2009.
\item Topology Seminar, The University of Texas at Austin, April 13, 2009.
\item Groups and Dynamics Seminar, Texas A\&M University, March 25, 2009.
\item Topology Seminar, The University of Texas at Austin, October 27, 2008.
\item Groups and Infinite Graphs, Erwin Schroedinger International Institute, Austria, August 26, 2008.
\item Topology Seminar, Seoul National University, Korea, June 2, 2008.
\item Topology Seminar, The University of Texas at Austin, January 28, 2008.
\item Joint Postdoc Seminar, Mathematics Sciences Research Institute, October 19 2007.
\item Group Actions Seminar, Yale University, October 16, 2006.
\item Student Seminar (exposition), Yale University, May 1, 2004.
\end{enumerate}
\end{document}
